\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-20 paper.tex
Added application for OP _RETURN analysis.

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{xcolor}

@@

 \textcolor{red}{\textit{If appropriate, you should describe your implementation and experimental results. Explain how to interpret your numbers and results if applicable.}}

\textcolor{blue}{[Motivation for the application cases we chose.]}

@@

For the Bitcoin network to function properly, it is important that the network form a single connected component. A type of attack against the network is to try and cut some nodes from the rest of the network, and then ``double-spend'' the same amount of money on the two disconnected components, which will both accept the transactions. Such a cut can be achieved by performing a DoS attack against a group of nodes that collectively ensure connectivity between two otherwise separated subnetworks. One way to perform a DoS attack could be to have a node attempt to evaluate a Script program with an unreasonable execution time. It is therefore important to guarantee that a Script program will terminate within a certain amount of steps.

Using the small-step semantics defined in Section 3 of the appendix, we see that no reduction rule yields its entire input, as was the case with the \texttt{while} local reduction rule in IMP. That is to say, no recursion is allowed. At most a proper subset of the input is conserved after applying the rule, when it is not completely replaced by \texttt{OP\_NOP}, Script's equivalent of the \texttt{skip} command. This guarantees that every small-step reduction progresses towards termination of the program. Furthermore, the global reduction rule trivially entails that for any program that is not only \texttt{OP\_NOP}, there exists a unique context reducible by a local reduction rule. Thus we have that every Script program halts.

@@

\subsection{Previous versions of Script allowed undesirable programs}
Here we prove how previous states were problematic

\subsection{The Script command set could be reduced without loss of expressiveness}
Here we prove that some commands are redundant. Must exaplin why this can be desirable sometimes, but also why some of them are clearly uselessly redundant.

>>>>

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{xcolor}

@@

@@

\subsubsection{Background}
For the Bitcoin network to function properly, it is important that the network form a single connected component. A type of attack against the network is to try and cut some nodes from the rest of the network, and then ``double-spend'' the same amount of money on the two disconnected components, which will both accept the transactions. Such a cut can be achieved by performing a DoS attack against a group of nodes that collectively ensure connectivity between two otherwise separated subnetworks. One way to perform a DoS attack could be to have a node attempt to evaluate a Script program with an unreasonable execution time. It is therefore important to guarantee that a Script program will terminate within a certain amount of steps.

\subsubsection{Analysis}
Using the small-step semantics defined in Section 3 of the appendix, we see that no reduction rule yields its entire input, as was the case with the \texttt{while} local reduction rule in IMP. That is to say, no recursion is allowed. At most a proper subset of the input is conserved after applying the rule, when it is not completely replaced by \texttt{OP\_NOP}, Script's equivalent of the \texttt{skip} command. This guarantees that every small-step reduction progresses towards termination of the program. Furthermore, the global reduction rule trivially entails that for any program that is not only \texttt{OP\_NOP}, there exists a unique context reducible by a local reduction rule. Thus we have that every Script program halts.

@@

\subsection{Previous versions of Script allowed skeleton key scripts}

\subsubsection{Background}
The way an amount on Bitcoin is spent on the network is by evaluating to $\sigma[V=valid]$\footnote{See Appendix section 2 for a description of state configurations.} the concatenation $C = BA$ of a locking script A, provided by the payer, and an unlocking script B provided by the recipient. The intended scenario is that $A$ will contain a validation condition, which will check whether the output of $B$ is adequate. Typically, $B$ will have to provide a hash that proves they are the intended recipient of the money spent by the payer, and $A$ will know what to expect as a proof. In that way, $A$ is a guarantee to the payer that the money can only be received by the intended recipient. However, a careless definition of the \texttt{OP\_RETURN} opcode in previous versions of Script made it possible to program skeleton key scripts that could spend any amount of money, without proving the recipient's identity.

\subsubsection{Analysis}
A skeleton script would have the following property: 
$$\exists B. \forall A. \hspace{1.5mm} BA \Downarrow \sigma[V=valid]$$

This is equivalent to saying that either (1) $B$ is such that for any $A$, $BA$ evaluates to a valid state, or (2) $B$ evaluates to a state from which any $A$ will evaluate to a valid state. Case (2) was never possible, since one could write a script $A = \texttt{OP\_0}$, that pushes 0 on the stack. Upon normal program termination, if the top stack value is 0, then the program is deemed invalid. Thus for this $A$ there is no script $B$ such that $BA \Downarrow \sigma[V=valid]$. Case (1), however, was made possible by the semantics of \texttt{OP\_RETURN} prior to July 31 2010. In local reduction rule form, \texttt{OP\_RETURN} was defined as follows:
%
$$<\texttt{OP\_RETURN com}, \sigma> \hspace{3mm} \longrightarrow \hspace{3mm} <\texttt{OP\_NOP}, \sigma>$$
%
Evaluating \texttt{OP\_RETURN} results in the immediate termination of the program, \textit{without any changes to the state}. Consider now a script $B = \texttt{OP\_1 OP\_RETURN}$, and the evaluation of $BA$ for any arbitrary script $A$:

\begin{enumerate}
  \item \texttt{1} is pushed onto the stack
  \item \texttt{OP\_RETURN} triggers program termination
  \item The top stack value is nonzero, and so the program is deemed valid
\end{enumerate}

Clearly, that such a script was possible completely defeated the transaction validation process. \texttt{OP\_RETURN} semantics were subsequently changed to the following:
%
$$<\texttt{OP\_RETURN com}, \sigma> \hspace{1mm} \longrightarrow \hspace{1mm} <\texttt{OP\_NOP}, \sigma[V=invalid]>$$
%
thus ensuring that its evaluation in a script invariably resulted in a rejected transaction.
As no other command in the language can cause early termination of the program with a valid state, we can now say that there exists no skeleton key script that could serve to unlock any arbitrary locking script.

\subsection{The Script command set could be reduced without loss of expressiveness}
Here we prove that some commands are redundant. Must explain why this can be desirable sometimes, but also why some of them are clearly uselessly redundant.
